Journey: A Study of Scalabilty of Memory Management in Linux (TODO: should we get a new title?)

### 2017-04-28 paper.tex
add mmap latency conclusion

>>>>

The latency of mapping memory region is lowest when the new memory is allocated
next to an already allocated block. This latency is the worst when an already mapped region
is to be expanded. We suspect that a lot of real world applications to show the fragmented 
behavior when they need to expand their existing data structures. This furher highlights
the imporance of optimistically leaving empty spaces around the allocated regions to 
speed up memory expension. This would particularly be useful for performance crucial applications
running atop compute infrastructures where memory is not a scarce resource.
